Are Transformed Low Discrepancy Points Also Low Discrepancy?

### 2019-05-26 InvPts_verB.tex

\newcommand{\blind}{1}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{pro}{Proposition}
\newtheorem{defn}{Definition}
\newtheorem{rmk}{Remark}
\newtheorem{cor}{Corollary}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\naturals}{\mathbb{R}}
\newcommand{\va}{\boldsymbol{a}}
\newcommand{\vb}{\boldsymbol{b}}
\newcommand{\vc}{\boldsymbol{c}}
\newcommand{\vx}{\boldsymbol{x}}
\newcommand{\vX}{\boldsymbol{X}}
\newcommand{\vt}{\boldsymbol{t}}
\newcommand{\vz}{\boldsymbol{z}}
\newcommand{\vu}{\boldsymbol{u}}
\newcommand{\vv}{\boldsymbol{v}}
\newcommand{\vy}{\boldsymbol{y}}
\newcommand{\fraku}{\mathfrak{u}}
\newcommand{\frakv}{\mathfrak{v}}
\newcommand{\mX}{{\mathsf X}}
\newcommand{\vinfty}{\boldsymbol{\infty}}
\newcommand{\vzero}{\boldsymbol{0}}
\newcommand{\vPsi}{\boldsymbol{\Psi}}
\newcommand{\dif}{{\rm d}}
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator*{\argmax}{argmax}
\newcommand{\Udes}{\mathcal{U}}
\newcommand{\Xdes}{\mathcal{X}}
\newcommand{\FXdes}{F_{\Xdes}}
\newcommand{\cm}{\mathcal{M}}
\newcommand{\ch}{\mathcal{H}}
\newcommand{\MATLAB}{\textsc{Matlab}\xspace}
\newcommand{\Ftar}{F}
\newcommand{\ftar}{\varrho}
\newcommand{\cube}{\ensuremath{(0,1)^d}}
\newcommand{\bbone}{\mathbbm{1}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
\newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
\DeclareMathOperator{\cov}{cov}
\DeclareMathOperator{\err}{err}
\newcommand{\unif}{\textup{unif}}
\newcommand{\normal}{\textup{normal}}
\newcommand{\frakd}{\mathfrak{d}}
\newcommand{\tK}{\widetilde{K}}
\newcommand{\tOmega}{\widetilde{\Omega}}
\newcommand{\Order}{\mathcal{O}}

@@

For kernels of product form, \eqref{eq:prodkernel}, and target distributions with independent marginals, the formula for the squared discrepancy in \eqref{eq:discDef} becomes
\begin{align}
\nonumber
    D^2(\Xdes,\rho,K)  & = c^d  - \frac 2N \sum_{i=1}^N H(\vx_{i}) + \frac{1}{N^2}  \sum_{i,j=1}^N K(\vx_{i},x_{j}),
    \intertext{where}
    c & = \int_{\Omega_k \times \Omega_k} \tK_k(t_k,x_k) \, \varrho_k(t) \varrho_k (x) \, \dif t\dif x, \\
    H(\vx) = \prod_{k=1}^d [1+ h(x_{k})]
    h(x) & = \int_{\Omega_k} \tK_k(t,x)  \, \varrho_k(t) \, \dif t.
\end{align}
For a standard multivariate normal target distribution and the kernel defined in \eqref{eq:OrigKernel}, we have
\begin{align*}
c &= 1+\sqrt{\frac{2}{\pi}}, \\
h(x) &= \frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x|-x[\Phi(x)-1/2]-\phi(x),\\
\tK(t,x) &= \frac{1}{2} (|t|+ |x|- |x-t|).
\end{align*}

>>>>

\newcommand{\blind}{1}
\newtheorem{lem}{Lemma}
\newtheorem{thm}{Theorem}
\newtheorem{pro}{Proposition}
\newtheorem{defn}{Definition}
\newtheorem{rmk}{Remark}
\newtheorem{cor}{Corollary}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\naturals}{\mathbb{R}}
\newcommand{\va}{\boldsymbol{a}}
\newcommand{\vb}{\boldsymbol{b}}
\newcommand{\vc}{\boldsymbol{c}}
\newcommand{\vx}{\boldsymbol{x}}
\newcommand{\vX}{\boldsymbol{X}}
\newcommand{\vt}{\boldsymbol{t}}
\newcommand{\vz}{\boldsymbol{z}}
\newcommand{\vu}{\boldsymbol{u}}
\newcommand{\vv}{\boldsymbol{v}}
\newcommand{\vy}{\boldsymbol{y}}
\newcommand{\fraku}{\mathfrak{u}}
\newcommand{\frakv}{\mathfrak{v}}
\newcommand{\mX}{{\mathsf X}}
\newcommand{\vinfty}{\boldsymbol{\infty}}
\newcommand{\vzero}{\boldsymbol{0}}
\newcommand{\vPsi}{\boldsymbol{\Psi}}
\newcommand{\dif}{{\rm d}}
\DeclareMathOperator{\sign}{sign}
\DeclareMathOperator*{\argmax}{argmax}
\newcommand{\Udes}{\mathcal{U}}
\newcommand{\Xdes}{\mathcal{X}}
\newcommand{\FXdes}{F_{\Xdes}}
\newcommand{\cm}{\mathcal{M}}
\newcommand{\ch}{\mathcal{H}}
\newcommand{\MATLAB}{\textsc{Matlab}\xspace}
\newcommand{\Ftar}{F}
\newcommand{\ftar}{\varrho}
\newcommand{\cube}{\ensuremath{(0,1)^d}}
\newcommand{\bbone}{\mathbbm{1}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\ip}[3][{}]{\ensuremath{\left \langle #2, #3 \right \rangle_{#1}}}
\newcommand{\norm}[2][{}]{\ensuremath{\left \lVert #2 \right \rVert}_{#1}}
\DeclareMathOperator{\cov}{cov}
\DeclareMathOperator{\err}{err}
\newcommand{\unif}{\textup{unif}}
\newcommand{\normal}{\textup{normal}}
\newcommand{\frakd}{\mathfrak{d}}
\newcommand{\tK}{\widetilde{K}}
\newcommand{\tOmega}{\widetilde{\Omega}}
\newcommand{\tvarrho}{\widetilde{\varrho}}
\newcommand{\Order}{\mathcal{O}}

@@

For kernels of product form, \eqref{eq:prodkernel}, and target distributions with independent and identical marginals, the formula for the squared discrepancy in \eqref{eq:discDef} becomes
\begin{align}
\nonumber
    D^2(\Xdes,\rho,K)  & = c^d  - \frac 2N \sum_{i=1}^N H(\vx_{i}) + \frac{1}{N^2}  \sum_{i,j=1}^N K(\vx_{i},x_{j}),
    \intertext{where}
    c & = \int_{\tOmega \times \tOmega} \tK(t_k,x_k) \, \tvarrho(t) \tvarrho (x) \, \dif t\dif x, \\
    h(x) & = \int_{\tOmega} \tK_k(t,x)  \, \tvarrho(t) \, \dif t.
    c & = \int_{\Omega_k \times \Omega_k} \tK_k(t_k,x_k) \, \varrho_k(t) \varrho_k (x) \, \dif t\dif x, \\
    H(\vx) = \prod_{k=1}^d [1+ h(x_{k})]
    h(x) & = \int_{\Omega_k} \tK_k(t,x)  \, \varrho_k(t) \, \dif t.
\end{align}
For a standard multivariate normal target distribution and the kernel defined in \eqref{eq:OrigKernel}, we have
\begin{align*}
c &= 1+\sqrt{\frac{2}{\pi}}, \\
h(x) &= \frac{1}{\sqrt{2\pi}}+\frac{1}{2}|x|-x[\Phi(x)-1/2]-\phi(x),\\
\tK(t,x) &= \frac{1}{2} (|t|+ |x|- |x-t|).
\end{align*}
